Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-09-23 cover-letter/cover-letter.Rmd
minor changes

The manuscript is original, and no part has been published before, nor is any part of it under consideration for publication at another journal. A preprint has been made available at arXiv and submitted to be added to Monash EBS working papers.

>>>>

The manuscript is original. A preprint has been made available at arXiv and Monash EBS working paper series, but no part has been published before, nor is any part of it under consideration for publication at another journal.
